\Huge{Complex State Management with Immutability}

### 2022-02-18 Paper.tex
migration

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{color}

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\title{Immutability for Better State Management}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\begin{abstract}
    Recent growing demand for fault-tolerant, scalable, distributed systems has made some mainstream software architectures and patterns obsolete or rather harder to come by, and thus came the rise of stateless and functional solutions based on data immutability which has already been the cornerstone of "Big Data"

\end{abstract}

\begin{IEEEkeywords}
immutable data structures, functional programming, algorithm design
\end{IEEEkeywords}

\section{Introduction}
% src
% Immutability an Empirical Study in Scala.pdf
When something is immutable, we say that it cannot be changed or that it is unchangeable. The definition
of an immutable object in an object-oriented programming language is an object that has a state
that cannot be mutated once instantiated (created). Moreover, an immutable class is a class whose instances
cannot be mutated, meaning that there are no methods in the class that can mutate an instance
of it. Classes that are not immutable can, however, have instances of it that are immutable.

@@

\end{lstlisting}
this behavior is implemented in some languages is what's known as Function0 that is "a function without parameters" but this would be somewhat expensive since you have to pack (copy) the closure
%TODO: explain what a closure is ...
of the function with it to achieve predictable behavior contrary to just keeping references. but if the data is immutable it would make sense to only pack references this is what's referred to as laziness

@@

% chanllenging
% modularity

% bref on 
% determenistic concurrency
% reactiveity
% modernday statless deployment
% 	docker or distributed or actor
% 	strong endpoint devices

>>>>

%PLEASE COPY THE FILE AND EDIT THE COPY, DO NOT EDIT THIS FILE!!!

\documentclass[12pt,twoside]{article}
\usepackage[a4paper,width=150mm,top=30mm,bottom=30mm,bindingoffset=10mm]{geometry}
\linespread{1}
\usepackage[utf8]{inputenc} %Standard diacritics in Romance languages (accents, umlauts)
\usepackage{times} %Uses Times New Roman font
\usepackage{wasysym}
\usepackage{diagbox}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[style=authoryear-icomp,natbib=true,sortcites=true]{biblatex}% natbib=true so we can use natbib commands with biblatex
% Also: authoryear-icomp is used so that when you cite the same author with different years, you get "according to Herberger (2002, 2004)" rather than "according to Herberger (2002), Herberger (2004)"
\addbibresource{refs.bib}

\usepackage{xpatch}
\usepackage{listings}
\usepackage{color}

@@

\usepackage[tiny]{titlesec}
\titleformat{\subsection}{}{\thesubsection}{1em}{\itshape}
\titleformat{\subsubsection}{}{\thesubsubsection}{1em}{\itshape}
\titlelabel{\thetitle.\quad}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE]{\thepage \hspace{3mm} \small Isogloss YEAR, ISSUE/NR}
\fancyhead[RE]{\small Author}
\fancyhead[LO]{\small Title of paper}
\fancyhead[RO]{\small Isogloss YEAR, 1/2 \normalsize \thepage}
\fancyfoot{}
%\setcounter{page}{23} %This sets the initial page at a number other than 1 (in this case 23).

\fancypagestyle{first}{
	\fancyhead{}
	\fancyhead[L]{\small ISSN 2835-4138 (digital)\\https://doi.org/10.5565/rev/isogloss.\\{}}
	\fancyhead[R]{\small Isogloss YEAR, ISSUE/NR\\PAGES\\{}}
	\fancyfoot{}}
	%don't worry about the headers, we will compile them

\newcommand{\pref}[1]{(\ref{#1})} % If you use \ref{xx}, the reference in the text appears without parentheses: "as we see in 1, ..." instead of "as we see in (1)...". So we create a new command: instead of \ref, call \pref (Parentheses REFerence) which specifies that any cross references to xx appear in parentheses.

\usepackage{tipa} %for IPA
\usepackage{phonrule} %for phonological rules
\usepackage[nocenter]{qtree} %for trees
\usepackage{gb4e} %for examples and glossing

\usepackage[normalem]{ulem} %STRIKETHROUGH TEXT

\usepackage{authblk,etoolbox}
\renewcommand\Authfont{\Large}
\renewcommand\Affilfont{\normalsize}

\makeatletter
% patch \maketitle so that it doesn't center
\patchcmd{\@maketitle}{center}{flushleft}{}{}
\patchcmd{\@maketitle}{center}{flushleft}{}{}
% patch \maketitle so that the font size for the title is normal
\patchcmd{\@maketitle}{\LARGE}{\normalsize}{}{}

\def\maketitle{{%
		\renewenvironment{tabular}[2][]
		{\begin{flushleft}}
			{\end{flushleft}}
		\AB@maketitle}}
\makeatother

\title{\Huge{Complex State Management with Immutability}}
\author{Nassouh AlOlabi} \affil{anon \\email} 
\setlength{\affilsep}{1pt}
\date{}

%IF THERE ARE TWO AUTHORS:
%\title{\Huge{Patterns of syntactic microvariation: the case of European Portuguese}}
%\author{Noam Chomsky} \affil{Massachusetts Institute of Technology\\noam.chomsky@mit.edu} 
%\author{Howard Lasnik} \affil{University of Maryland\\howard.lasnik@umd.edu}
%\setlength{\affilsep}{1pt}
%\date{}

@@

@@

\thispagestyle{first}

\vspace{0.5cm}

\hfill Received: 20-01-2034

\hfill Accepted: 21-01-2034

\hfill Published: 22-01-2034

\vspace{1cm}

\noindent \textbf{How to cite} Leave blank

\vspace{1.5cm}

\noindent \textbf{Abstract}
\begin{center}
 	\line(1,0){430}
\end{center}
\vspace{-0,3cm}
\noindent Recent growing demand for fault-tolerant, scalable, distributed systems has made some mainstream software architectures and patterns obsolete or rather harder to come by, and thus came the rise of stateless and functional solutions based on data immutability which has already been the cornerstone of "Big Data"

\vspace{5mm}

\noindent \textbf{Keywords:} immutable data structures, functional programming, algorithm design

\vspace{4mm}
\begin{center}
	\line(1,0){430}
\end{center}

%\begin{center}
%	\textbf{Table of Contents}
%\end{center}

%\begin{large}
%\begin{center}
	%\begin{tabular}{c c}
%		1. Section 1 & 4. Section 4\\
%		2. Section 2 & 5. Section 5\\
%		3. Section 3 & 6. Section 6
%	\end{tabular}
%\end{center}
%\end{large}

\newpage
\tableofcontents
\newpage

\section{Introduction}

% src
% Immutability an Empirical Study in Scala.pdf
When something is immutable, we say that it cannot be changed or that it is unchangeable. The definition
of an immutable object in an object-oriented programming language is an object that has a state
that cannot be mutated once instantiated (created). Moreover, an immutable class is a class whose instances
cannot be mutated, meaning that there are no methods in the class that can mutate an instance
of it. Classes that are not immutable can, however, have instances of it that are immutable.

@@

\end{lstlisting}
this behavior is implemented in some languages is what's known as Function0 that is "a function without parameters" but this would be somewhat expensive since you have to pack (copy) the closure

%TODO: explain what a closure is ...
of the function with it to achieve predictable behavior contrary to just keeping references. but if the data is immutable it would make sense to only pack references this is what's referred to as laziness

@@

% chanllenging
% modularity
% time travelling debugger
% bref on 
% determenistic concurrency
% reactiveity
% modernday statless deployment
% 	docker or distributed or actor
% 	strong endpoint devices

\section*{Acknowledgements}
The author wishes to thank Blabla and bla

\printbibliography
